[dcpo_demsupport]

### 2020-06-27 paper/dcpo_demsupport.Rmd
specify arguments correctly for dcpo_replication_input

dcpo_replication_input <- DCPOtools::format_dcpo(claassen_input_raw1)
save(dcpo_replication_input, file = here::here("data", "dcpo_replication_input.rda"))
```

@@

```{r comparison_table}
load("data/claassen_m5_x_pred.rda")

@@

```{r validation}
# load(here::here("data", "validation_table.rda"))
# 
# validation_table
```

@@

## Results
DCPO results here

>>>>

dcpo_replication_input <- DCPOtools::format_dcpo(claassen_input_raw1,
                                                 scale_q = "church_lb",
                                                 scale_cp = 2)
save(dcpo_replication_input, file = here::here("data", "dcpo_replication_input.rda"))
```

@@

```{r comparison_table}
load(here::here("data", "claassen_m5_x_pred.rda"))

@@

<!-- We will probably want to just want to summarize results in writing instead of a table, given that we're comparing just two models, rather than three, and space constraints -->

@@

## Results

### Claassen with uncertainty

### DCPO replication (with uncertainty, of course)

### DCPO, with lots more data
